Chapter 4

### 2021-04-26 thesis_chapter_4.Rmd
updates
chapter 4 script

# Make table based on new entries
site_surface_area <- morph_data
site_surface_area <- flextable(data = site_surface_area)
site_surface_area <- theme_zebra(site_surface_area, odd_header = "transparent", even_header = "transparent")
site_surface_area <- align(x= site_surface_area, align = "center", part = "all")
#area_table <- set_header_labels(area_table, Plant.characteristic = "Plant characteristic", Approximate.shape = "Approximate shape", Equation.used = "Equation Used", Plant.dimensions = "Plant dimensions")
#area_table <- set_header_labels(area_table, Ac.Minimum = "Ac Minimum", Ac.Mean = "Ac Mean", Ac.Maximum = "Ac Maximum")
site_surface_area <- set_table_properties(site_surface_area, width = 1, layout = "autofit")
#site_surface_area <- set_caption(site_surface_area, "Table 2:Summary of the atrributes and estimates used to calculate the overall surface area of Kommetjie kelp individuals used in the various simulation.")
site_surface_area
```

>>>>

# Calculate the total mass of kelp individual based on site morphological characteristics

morph_data$total_mass <- with(morph_data, (frond_mass*6) + (stipe_mass) )

# Make table based on new entries
site_surface_area <- morph_data
site_surface_area <- flextable(data = site_surface_area)
#site_surface_area <- theme_zebra(site_surface_area, odd_header = "transparent", even_header = "transparent")
site_surface_area <- align(x= site_surface_area, align = "center", part = "all")
#area_table <- set_header_labels(area_table, Plant.characteristic = "Plant characteristic", Approximate.shape = "Approximate shape", Equation.used = "Equation Used", Plant.dimensions = "Plant dimensions")
#area_table <- set_header_labels(area_table, Ac.Minimum = "Ac Minimum", Ac.Mean = "Ac Mean", Ac.Maximum = "Ac Maximum")
site_surface_area <- set_table_properties(site_surface_area, width = 1, layout = "autofit")
#site_surface_area <- set_caption(site_surface_area, "Table 2:Summary of the atrributes and estimates used to calculate the overall surface area of Kommetjie kelp individuals used in the various simulation.")
site_surface_area
```

```{r, warning=FALSE, message=FALSE, echo = FALSE}

houtbay <- tidync("OceanParcels/trajectory_data/chapter_4_output/houtbay.nc") %>%
  hyper_tibble() %>%
  dplyr::select(trajectory, lon, lat, time, distance, age) %>%
  dplyr::rename(t = time) %>%
  mutate(t = as.POSIXct(t, origin = "2020-01-01 00:00:00"))

houtbay_mean <- houtbay %>% # calculate mean trajectory
  group_by(t) %>% 
  summarise(across(lon:lat, mean, na.rm= TRUE))

houtbay$site <- "Hout Bay" 
houtbay_mean$site <- "Hout Bay"

kommetjie <- tidync("OceanParcels/trajectory_data/chapter_4_output/kommetjie.nc") %>%
  hyper_tibble() %>%
  dplyr::select(trajectory, lon, lat, time, distance, age) %>%
  dplyr::rename(t = time) %>%
  mutate(t = as.POSIXct(t, origin = "2020-01-01 00:00:00"))

kommetjie_mean <- kommetjie %>% # calculate mean trajectory
  group_by(t) %>% 
  summarise(across(lon:lat, mean, na.rm= TRUE))

kommetjie$site <- "kommetjie" 
kommetjie_mean$site <- "kommetjie"

soetwater <- tidync("OceanParcels/trajectory_data/chapter_4_output/soetwater.nc") %>%
  hyper_tibble() %>%
  dplyr::select(trajectory, lon, lat, time, distance, age) %>%
  dplyr::rename(t = time) %>%
  mutate(t = as.POSIXct(t, origin = "2020-01-01 00:00:00"))

soetwater_mean <- soetwater %>% # calculate mean trajectory
  group_by(t) %>% 
  summarise(across(lon:lat, mean, na.rm= TRUE))

soetwater$site <- "Soetwater" 
soetwater_mean$site <- "Soetwater"

millers <- tidync("OceanParcels/trajectory_data/chapter_4_output/millers.nc") %>%
  hyper_tibble() %>%
  dplyr::select(trajectory, lon, lat, time, distance, age) %>%
  dplyr::rename(t = time) %>%
  mutate(t = as.POSIXct(t, origin = "2020-01-01 00:00:00"))

millers_mean <- millers %>% # calculate mean trajectory
  group_by(t) %>% 
  summarise(across(lon:lat, mean, na.rm= TRUE))

millers$site <- "millers" 
millers_mean$site <- "millers"

total_data <- rbind(houtbay, soetwater, kommetjie, millers)
total_data_mean <- rbind(houtbay_mean, soetwater_mean,kommetjie_mean, millers_mean)
```

## Mean trajectory

```{r, message=FALSE, warning=FALSE, echo=FALSE}

library(ggplot2)

## Coastline of Southern Africa
load("map/south_africa_coast_hi_res.Rdata")

mean_traj_site <- ggplot() + 
  geom_polygon(data = south_africa_coast_hi_res, aes(x = lon, y = lat, group = PID),
               size = 1.0, colour = "black", fill = NA) +
  geom_path(data = total_data_mean, aes(x = lon, y = lat, colour = site)) +
  xlab("Longtitude") + 
  ylab("Latitude") + 
  ggtitle("") +
  theme(plot.title = element_text(hjust = 0.5)) +
  theme_bw()

```{r echo=FALSE, message=FALSE, warning=FALSE}

mean_traj_site

## Density comparisons

```{r, message=FALSE, echo=FALSE, warning=FALSE}

## Coastline of Southern Africa
load("map/south_africa_coast_hi_res.Rdata")

heatmap_houtbay <- ggplot() +
  geom_polygon(data = south_africa_coast_hi_res, aes(x = lon, y = lat, group =    PID), size = 1.0, colour = "black", fill = NA) +
  geom_hex(data = houtbay, bins = 80, aes(x = lon, y = lat), legend = FALSE) +  
  scale_fill_continuous(type = "gradient", limits = c(1, 1000000)) +
  geom_path(data = houtbay_mean,aes(x = lon, y = lat, color = 'red'),             show.legend = FALSE) +
  #coord_cartesian(xlim = c(14, 20), ylim = c(-35, -30)) + 
  xlab("Longtitude") + 
  ylab("Latitude") + 
  ggtitle("HoutBay") +
  guides(fill=guide_legend(title="Number of particles")) +
  theme_bw() +
  theme(plot.title = element_text(hjust = 0.5))

heatmap_komm <- ggplot() +
  geom_polygon(data = south_africa_coast_hi_res, aes(x = lon, y = lat, group =    PID), size = 1.0, colour = "black", fill = NA) +
  #geom_bin2d(data = p_RK4, bins = 80, aes(x = lon, y = lat)) +
  geom_hex(data = kommetjie, bins = 80, aes(x = lon, y = lat), legend = FALSE) +   scale_fill_continuous(type = "gradient", limits = c(1, 1000000)) +
  geom_path(data = kommetjie_mean,aes(x = lon, y = lat, color = 'red'),           show.legend = FALSE) +
  #coord_cartesian(xlim = c(14, 20), ylim = c(-35, -30)) + 
  xlab("Longtitude") + 
  ylab("Latitude") + 
  ggtitle("Kommetjie") +
  guides(fill=guide_legend(title="Number of particles")) +
  theme_bw() +
  theme(plot.title = element_text(hjust = 0.5))

heatmap_soetwater <- ggplot() +
  geom_polygon(data = south_africa_coast_hi_res, aes(x = lon, y = lat, group =    PID), size = 1.0, colour = "black", fill = NA) +
  #geom_bin2d(data = p_RK4, bins = 80, aes(x = lon, y = lat)) +
  geom_hex(data = soetwater, bins = 80, aes(x = lon, y = lat), legend = FALSE) +
  scale_fill_continuous(type = "gradient", limits = c(1, 1000000)) +
  geom_path(data = soetwater_mean,aes(x = lon, y = lat, color = 'red'),           show.legend = FALSE) +
  #coord_cartesian(xlim = c(14, 20), ylim = c(-35, -30)) + 
  xlab("Longtitude") + 
  ylab("Latitude") + 
  ggtitle("Soetwater") +
  guides(fill=guide_legend(title="Number of particles")) +
  theme_bw() +
  theme(plot.title = element_text(hjust = 0.5))

heatmap_soetwater <- ggplot() +
  geom_polygon(data = south_africa_coast_hi_res, aes(x = lon, y = lat, group =    PID), size = 1.0, colour = "black", fill = NA) +
  #geom_bin2d(data = p_RK4, bins = 80, aes(x = lon, y = lat)) +
  geom_hex(data = soetwater, bins = 80, aes(x = lon, y = lat), legend = FALSE) +
  scale_fill_continuous(type = "gradient", limits = c(1, 1000000)) +
  geom_path(data = soetwater_mean,aes(x = lon, y = lat, color = 'red'),           show.legend = FALSE) +
  #coord_cartesian(xlim = c(14, 20), ylim = c(-35, -30)) + 
  xlab("Longtitude") + 
  ylab("Latitude") + 
  ggtitle("Kommetjie") +
  guides(fill=guide_legend(title="Number of particles")) +
  theme_bw() +
  theme(plot.title = element_text(hjust = 0.5))

heatmap_millers <- ggplot() +
  geom_polygon(data = south_africa_coast_hi_res, aes(x = lon, y = lat, group =    PID), size = 1.0, colour = "black", fill = NA) +
  #geom_bin2d(data = p_RK4, bins = 80, aes(x = lon, y = lat)) +
  geom_hex(data = millers, bins = 80, aes(x = lon, y = lat), legend = FALSE) +  
  scale_fill_continuous(type = "gradient", limits = c(1, 1000000)) +
  geom_path(data = millers_mean,aes(x = lon, y = lat, color = 'red'),             show.legend = FALSE) +
  #coord_cartesian(xlim = c(14, 20), ylim = c(-35, -30)) + 
  xlab("Longtitude") + 
  ylab("Latitude") + 
  ggtitle("Millers") +
  guides(fill=guide_legend(title="Number of particles")) +
  theme_bw() +
  theme(plot.title = element_text(hjust = 0.5))

```{r echo=FALSE, message=FALSE, warning=FALSE}

ggarrange(heatmap_houtbay, heatmap_soetwater, heatmap_millers, ncol = 1, nrow = 3, font.label = list(size = 11, face = "bold"), common.legend = FALSE, legend = c("bottom"), labels = "AUTO", align = "hv")
```

```{r total heatmap, echo=FALSE, message=FALSE, warning=FALSE}

heatmap_total <- ggplot() +
  geom_polygon(data = south_africa_coast_hi_res, aes(x = lon, y = lat, group =    PID), size =    1.0, colour = "black", fill = NA) +
  #geom_bin2d(data = p_RK4, bins = 80, aes(x = lon, y = lat)) +
  geom_hex(data = total_data, bins = 80, aes(x = lon, y = lat), legend = FALSE) +  
  scale_fill_continuous(type = "gradient", limits = c(1, 19000000)) +
  geom_path(data = total_data_mean,aes(x = lon, y = lat, color = 'red'),show.legend = FALSE) +
  geom_rect(data = south_africa_coast_hi_res,aes(xmin=10, xmax=18.4, ymin=-33, ymax=-33.5),           inherit.aes = FALSE, fill = NA, colour =    "red", size = 1.5) +
  geom_rect(data = south_africa_coast_hi_res,aes(xmin=10, xmax=18.4, ymin=-33.5, ymax=-34.0),           inherit.aes = FALSE, fill = NA, colour =    "green", size = 1.5) +
  geom_rect(data = south_africa_coast_hi_res,aes(xmin=10, xmax=18.4, ymin=-34.0, ymax=-34.5),           inherit.aes = FALSE, fill = NA, colour =    "black", size = 1.5) +
  #coord_cartesian(xlim = c(14, 20), ylim = c(-35, -30)) + 
  xlab("Longtitude") + 
  ylab("Latitude") + 
  ggtitle("Millers") +
  guides(fill=guide_legend(title="Number of particles")) +
  theme_bw() +
  theme(plot.title = element_text(hjust = 0.5))
heatmap_total
```
